---
title: "GECD Bureaucracy Indicator Regressions with District Conditionals"
author: "Tom"
date: "September 21, 2020"
output: html_document
---

<br>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

#options(width = 300)

# packages
library(tidyverse)
library(readstata13)
library(sjPlot)
library(shiny)
library(summarytools)
library(miceadds)
library(estimatr)

# object with outcome variables
yvars <- c("student_knowledge",
           "ecd_student_knowledge",
           "inputs",
           "infrastructure",
           "intrinsic_motivation",
            "content_knowledge",
           "operational_manage",
           "instr_leader",
           "principal_knowl_score",
           "principal_manage",
           "bi",
           "national_learning_goals",
           "mandates_accountability",
           "quality_bureaucracy",
           "impartial_decision_making"
           )


condl <- c(
          "pct_urban",
          "med_age",
          "pct_school",
          "pct_lit",
          "pct_edu1",
          "pct_edu2",
          "pct_work",
          "pct_schoolage",
          "pct_elec" ,
          "pct_dwell",
          "enrolled",
          "ln_gdp",
          "ln_dist_n_stud"
  )

# Table Labels 
dvlab <- c("Student Knowledge", "ECD Knowledge", "Inputs", "Intrastructure", "Teacher Motivation", "Teacher Content Knowledge", "Operational Management", "Instructional Leadership", "Pricipal Knowledge", "Principal Management")

ivlab <- c("% Urban", "Literacy Rate", "% Schoolage", "% Electricity", "% Improved Dwelling", "Log N. Students in District", "Log GDP")

ivlabmain <- c("% Urban", "Literacy Rate", "% Schoolage", "% Electricity", "% Improved Dwelling", "Log N. Students in District")


ivlabmoz <- c("% Urban", "Literacy Rate", "% Schoolage", "% Electricity", "% Improved Dwelling", "Log N. Students in District")
dvlabmoz <- c("Student Knowledge", "Inputs", "Intrastructure", "Teacher Content Knowledge")




#load data
md <- read.dta13(file = "C:/Users/WB551206/OneDrive - WBG/Documents/Dashboard/global-education-dashboard/baseline/DataSets/final/merge_district_tdist.dta",
                 convert.factors = TRUE) %>%
  select(idschool, countryname, country, g1, g2, yvars, condl)

md.per <- md %>% 
  filter(countryname == "Peru")

md.jor <- md %>% 
  filter(countryname == "Jordan")

md.rwa <- md %>% 
  filter(countryname == "Rwanda")

md.moz <- md %>% 
  filter(countryname == "Mozambique")



```


# Model Specifications<br>
- Country Fixed Effects (coefficients omitted)
- School size Fixed Effects (coefficients omitted)
- Standard Errors clustered on District, specified to standard clustering in Stata
- District-level averages of: 
  1. Percent Urban ( % of surveyed Households classified as Urban)
  2. Literacy Rate
  3. Percent of population that is of school age (see technical note for details)
  4. Percent of households with access to electricity
  5. Percent of households with improved dwelling construction materials
  6. Natural Log of total enrolled students in the district
  7. Natural Log of school-area GDP (except for Mozambique)
  

## Technical Notes <br>
Percent Schoolage Population: To be consistent with other IPUMS age categorizations, the schoolage population is defined as the percent of the population from ages 6 through 14, inclusive. Age 14 was chosen as the top-value because IPUMS defines working-age population beginning at age 15. <br><br>

Percent of Households with Improved Dwelling construction: Materials classified as "improved" are Adobe and Stone: all others, such as straw, cloth, bamboo, etc wer considered "not improved". <br><br>

I have coded and prepared other similar variables that were not included in the model specification but could be interchanged as needed. <br>
1. Percent of Population that ever attended school <br>
2. Percent of Population that completed Primary School  <br>
3. Percent of Population that completed Secondary School<br>
4. Labor Force Participation<br>
5. District Median Age <br>

  


## Main findings <br>
1. The Overall Bureaucracy Index significantly predicts school infrastructure and teacher content knowledge. <br>
2. National Learning Goals predicts teacher level indicators <br>
3. Mandates and Accountability and Quality of Bureaucracy predict a handfull of school outcomes 
4. Otherwise, indicators for aggregate district wealth (dwelling) and existing infrastructure (Pct Electrified) are strong predictors of school outcomes in many, but not all, models

```{r models,  include=FALSE}
# run + store all regressions regressions as objects

# explanatory = bi
lm.bi.1 <- lm_robust(data = md,
   student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.2 <- lm_robust(data = md,
   ecd_student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.3 <- lm_robust(data = md,
   inputs ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.4 <- lm_robust(data = md,
   infrastructure ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.5 <- lm_robust(data = md,
   intrinsic_motivation ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.6 <- lm_robust(data = md,
   content_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.8 <- lm_robust(data = md,
   operational_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.9 <- lm_robust(data = md,
   instr_leader ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.10 <- lm_robust(data = md,
   principal_knowl_score ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.bi.11 <- lm_robust(data = md,
   principal_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")

# explanatory = nlg
lm.nlg.1 <- lm_robust(data = md,
   student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.2 <- lm_robust(data = md,
   ecd_student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.3 <- lm_robust(data = md,
   inputs ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.4 <- lm_robust(data = md,
   infrastructure ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.5 <- lm_robust(data = md,
   intrinsic_motivation ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.6 <- lm_robust(data = md,
   content_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.8 <- lm_robust(data = md,
   operational_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.9 <- lm_robust(data = md,
   instr_leader ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.10 <- lm_robust(data = md,
   principal_knowl_score ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.nlg.11 <- lm_robust(data = md,
   principal_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")

# explanatory = ma
lm.ma.1 <- lm_robust(data = md,
   student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.2 <- lm_robust(data = md,
   ecd_student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.3 <- lm_robust(data = md,
   inputs ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.4 <- lm_robust(data = md,
   infrastructure ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.5 <- lm_robust(data = md,
   intrinsic_motivation ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.6 <- lm_robust(data = md,
   content_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.8 <- lm_robust(data = md,
   operational_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.9 <- lm_robust(data = md,
   instr_leader ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.10 <- lm_robust(data = md,
   principal_knowl_score ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.ma.11 <- lm_robust(data = md,
   principal_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")


# explanatory = qb
lm.qb.1 <- lm_robust(data = md,
   student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.2 <- lm_robust(data = md,
   ecd_student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.3 <- lm_robust(data = md,
   inputs ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.4 <- lm_robust(data = md,
   infrastructure ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.5 <- lm_robust(data = md,
   intrinsic_motivation ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.6 <- lm_robust(data = md,
   content_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.8 <- lm_robust(data = md,
   operational_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.9 <- lm_robust(data = md,
   instr_leader ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.10 <- lm_robust(data = md,
   principal_knowl_score ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.qb.11 <- lm_robust(data = md,
   principal_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")

# explanatory = idm
lm.idm.1 <- lm_robust(data = md,
   student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.2 <- lm_robust(data = md,
   ecd_student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.3 <- lm_robust(data = md,
   inputs ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.4 <- lm_robust(data = md,
   infrastructure ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.5 <- lm_robust(data = md,
   intrinsic_motivation ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.6 <- lm_robust(data = md,
   content_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.8 <- lm_robust(data = md,
   operational_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.9 <- lm_robust(data = md,
   instr_leader ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.10 <- lm_robust(data = md,
   principal_knowl_score ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")
lm.idm.11 <- lm_robust(data = md,
   principal_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud  + as.factor(enrolled) + as.factor(countryname), clusters = g2, se_type = "stata")

```



```{r peru, warning=FALSE}


# explanatory = bi
lm.per.bi.1 <- lm_robust(data = md.per,
   student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.2 <- lm_robust(data = md.per,
   ecd_student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.3 <- lm_robust(data = md.per,
   inputs ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.4 <- lm_robust(data = md.per,
   infrastructure ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.5 <- lm_robust(data = md.per,
   intrinsic_motivation ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.6 <- lm_robust(data = md.per,
   content_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.8 <- lm_robust(data = md.per,
   operational_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.9 <- lm_robust(data = md.per,
   instr_leader ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.10 <- lm_robust(data = md.per,
   principal_knowl_score ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.bi.11 <- lm_robust(data = md.per,
   principal_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = nlg
lm.per.nlg.1 <- lm_robust(data = md.per,
   student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.2 <- lm_robust(data = md.per,
   ecd_student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.3 <- lm_robust(data = md.per,
   inputs ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.4 <- lm_robust(data = md.per,
   infrastructure ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.5 <- lm_robust(data = md.per,
   intrinsic_motivation ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.6 <- lm_robust(data = md.per,
   content_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.8 <- lm_robust(data = md.per,
   operational_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.9 <- lm_robust(data = md.per,
   instr_leader ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.10 <- lm_robust(data = md.per,
   principal_knowl_score ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.nlg.11 <- lm_robust(data = md.per,
   principal_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = ma
lm.per.ma.1 <- lm_robust(data = md.per,
   student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.2 <- lm_robust(data = md.per,
   ecd_student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.3 <- lm_robust(data = md.per,
   inputs ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.4 <- lm_robust(data = md.per,
   infrastructure ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.5 <- lm_robust(data = md.per,
   intrinsic_motivation ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.6 <- lm_robust(data = md.per,
   content_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.8 <- lm_robust(data = md.per,
   operational_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.9 <- lm_robust(data = md.per,
   instr_leader ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.10 <- lm_robust(data = md.per,
   principal_knowl_score ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.ma.11 <- lm_robust(data = md.per,
   principal_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


# explanatory = qb
lm.per.qb.1 <- lm_robust(data = md.per,
   student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.2 <- lm_robust(data = md.per,
   ecd_student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.3 <- lm_robust(data = md.per,
   inputs ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.4 <- lm_robust(data = md.per,
   infrastructure ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.5 <- lm_robust(data = md.per,
   intrinsic_motivation ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.6 <- lm_robust(data = md.per,
   content_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.8 <- lm_robust(data = md.per,
   operational_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.9 <- lm_robust(data = md.per,
   instr_leader ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.10 <- lm_robust(data = md.per,
   principal_knowl_score ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.qb.11 <- lm_robust(data = md.per,
   principal_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = idm
lm.per.idm.1 <- lm_robust(data = md.per,
   student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.2 <- lm_robust(data = md.per,
   ecd_student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.3 <- lm_robust(data = md.per,
   inputs ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.4 <- lm_robust(data = md.per,
   infrastructure ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.5 <- lm_robust(data = md.per,
   intrinsic_motivation ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.6 <- lm_robust(data = md.per,
   content_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.8 <- lm_robust(data = md.per,
   operational_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.9 <- lm_robust(data = md.per,
   instr_leader ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.10 <- lm_robust(data = md.per,
   principal_knowl_score ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.per.idm.11 <- lm_robust(data = md.per,
   principal_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


```

```{r jordan, warning=FALSE}


# explanatory = bi
lm.jor.bi.1 <- lm_robust(data = md.jor,
   student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.2 <- lm_robust(data = md.jor,
   ecd_student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.3 <- lm_robust(data = md.jor,
   inputs ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.4 <- lm_robust(data = md.jor,
   infrastructure ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.5 <- lm_robust(data = md.jor,
   intrinsic_motivation ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.6 <- lm_robust(data = md.jor,
   content_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.8 <- lm_robust(data = md.jor,
   operational_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.9 <- lm_robust(data = md.jor,
   instr_leader ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.10 <- lm_robust(data = md.jor,
   principal_knowl_score ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.bi.11 <- lm_robust(data = md.jor,
   principal_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = nlg
lm.jor.nlg.1 <- lm_robust(data = md.jor,
   student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.2 <- lm_robust(data = md.jor,
   ecd_student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.3 <- lm_robust(data = md.jor,
   inputs ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.4 <- lm_robust(data = md.jor,
   infrastructure ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.5 <- lm_robust(data = md.jor,
   intrinsic_motivation ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.6 <- lm_robust(data = md.jor,
   content_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.8 <- lm_robust(data = md.jor,
   operational_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.9 <- lm_robust(data = md.jor,
   instr_leader ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.10 <- lm_robust(data = md.jor,
   principal_knowl_score ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.nlg.11 <- lm_robust(data = md.jor,
   principal_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = ma
lm.jor.ma.1 <- lm_robust(data = md.jor,
   student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.2 <- lm_robust(data = md.jor,
   ecd_student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.3 <- lm_robust(data = md.jor,
   inputs ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.4 <- lm_robust(data = md.jor,
   infrastructure ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.5 <- lm_robust(data = md.jor,
   intrinsic_motivation ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.6 <- lm_robust(data = md.jor,
   content_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.8 <- lm_robust(data = md.jor,
   operational_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.9 <- lm_robust(data = md.jor,
   instr_leader ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.10 <- lm_robust(data = md.jor,
   principal_knowl_score ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.ma.11 <- lm_robust(data = md.jor,
   principal_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


# explanatory = qb
lm.jor.qb.1 <- lm_robust(data = md.jor,
   student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.2 <- lm_robust(data = md.jor,
   ecd_student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.3 <- lm_robust(data = md.jor,
   inputs ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.4 <- lm_robust(data = md.jor,
   infrastructure ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.5 <- lm_robust(data = md.jor,
   intrinsic_motivation ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.6 <- lm_robust(data = md.jor,
   content_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.8 <- lm_robust(data = md.jor,
   operational_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.9 <- lm_robust(data = md.jor,
   instr_leader ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.10 <- lm_robust(data = md.jor,
   principal_knowl_score ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.qb.11 <- lm_robust(data = md.jor,
   principal_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = idm
lm.jor.idm.1 <- lm_robust(data = md.jor,
   student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.2 <- lm_robust(data = md.jor,
   ecd_student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.3 <- lm_robust(data = md.jor,
   inputs ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.4 <- lm_robust(data = md.jor,
   infrastructure ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.5 <- lm_robust(data = md.jor,
   intrinsic_motivation ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.6 <- lm_robust(data = md.jor,
   content_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.8 <- lm_robust(data = md.jor,
   operational_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.9 <- lm_robust(data = md.jor,
   instr_leader ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.10 <- lm_robust(data = md.jor,
   principal_knowl_score ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.jor.idm.11 <- lm_robust(data = md.jor,
   principal_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


```

```{r rwanda, warning=FALSE}


# explanatory = bi
lm.rwa.bi.1 <- lm_robust(data = md.rwa,
   student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.2 <- lm_robust(data = md.rwa,
   ecd_student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.3 <- lm_robust(data = md.rwa,
   inputs ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.4 <- lm_robust(data = md.rwa,
   infrastructure ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.5 <- lm_robust(data = md.rwa,
   intrinsic_motivation ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.6 <- lm_robust(data = md.rwa,
   content_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.8 <- lm_robust(data = md.rwa,
   operational_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.9 <- lm_robust(data = md.rwa,
   instr_leader ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.10 <- lm_robust(data = md.rwa,
   principal_knowl_score ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.bi.11 <- lm_robust(data = md.rwa,
   principal_manage ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = nlg
lm.rwa.nlg.1 <- lm_robust(data = md.rwa,
   student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.2 <- lm_robust(data = md.rwa,
   ecd_student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.3 <- lm_robust(data = md.rwa,
   inputs ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.4 <- lm_robust(data = md.rwa,
   infrastructure ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.5 <- lm_robust(data = md.rwa,
   intrinsic_motivation ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.6 <- lm_robust(data = md.rwa,
   content_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.8 <- lm_robust(data = md.rwa,
   operational_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.9 <- lm_robust(data = md.rwa,
   instr_leader ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.10 <- lm_robust(data = md.rwa,
   principal_knowl_score ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.nlg.11 <- lm_robust(data = md.rwa,
   principal_manage ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = ma
lm.rwa.ma.1 <- lm_robust(data = md.rwa,
   student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.2 <- lm_robust(data = md.rwa,
   ecd_student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.3 <- lm_robust(data = md.rwa,
   inputs ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.4 <- lm_robust(data = md.rwa,
   infrastructure ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.5 <- lm_robust(data = md.rwa,
   intrinsic_motivation ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.6 <- lm_robust(data = md.rwa,
   content_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.8 <- lm_robust(data = md.rwa,
   operational_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.9 <- lm_robust(data = md.rwa,
   instr_leader ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.10 <- lm_robust(data = md.rwa,
   principal_knowl_score ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.ma.11 <- lm_robust(data = md.rwa,
   principal_manage ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


# explanatory = qb
lm.rwa.qb.1 <- lm_robust(data = md.rwa,
   student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.2 <- lm_robust(data = md.rwa,
   ecd_student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.3 <- lm_robust(data = md.rwa,
   inputs ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.4 <- lm_robust(data = md.rwa,
   infrastructure ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.5 <- lm_robust(data = md.rwa,
   intrinsic_motivation ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.6 <- lm_robust(data = md.rwa,
   content_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.8 <- lm_robust(data = md.rwa,
   operational_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.9 <- lm_robust(data = md.rwa,
   instr_leader ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.10 <- lm_robust(data = md.rwa,
   principal_knowl_score ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.qb.11 <- lm_robust(data = md.rwa,
   principal_manage ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")

# explanatory = idm
lm.rwa.idm.1 <- lm_robust(data = md.rwa,
   student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.2 <- lm_robust(data = md.rwa,
   ecd_student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.3 <- lm_robust(data = md.rwa,
   inputs ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.4 <- lm_robust(data = md.rwa,
   infrastructure ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.5 <- lm_robust(data = md.rwa,
   intrinsic_motivation ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.6 <- lm_robust(data = md.rwa,
   content_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.8 <- lm_robust(data = md.rwa,
   operational_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.9 <- lm_robust(data = md.rwa,
   instr_leader ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.10 <- lm_robust(data = md.rwa,
   principal_knowl_score ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")
lm.rwa.idm.11 <- lm_robust(data = md.rwa,
   principal_manage ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud + ln_gdp + as.factor(enrolled) , clusters = g2, se_type = "stata")


```

```{r mozambique, warning=FALSE}


# explanatory = bi
lm.moz.bi.1 <- lm_robust(data = md.moz,
   student_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.bi.3 <- lm_robust(data = md.moz,
   inputs ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.bi.4 <- lm_robust(data = md.moz,
   infrastructure ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.bi.6 <- lm_robust(data = md.moz,
   content_knowledge ~ bi + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")


# explanatory = nlg
lm.moz.nlg.1 <- lm_robust(data = md.moz,
   student_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.nlg.3 <- lm_robust(data = md.moz,
   inputs ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.nlg.4 <- lm_robust(data = md.moz,
   infrastructure ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.nlg.6 <- lm_robust(data = md.moz,
   content_knowledge ~ national_learning_goals + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")


# explanatory = ma
lm.moz.ma.1 <- lm_robust(data = md.moz,
   student_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.ma.3 <- lm_robust(data = md.moz,
   inputs ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.ma.4 <- lm_robust(data = md.moz,
   infrastructure ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.ma.6 <- lm_robust(data = md.moz,
   content_knowledge ~ mandates_accountability + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")



# explanatory = qb
lm.moz.qb.1 <- lm_robust(data = md.moz,
   student_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.qb.3 <- lm_robust(data = md.moz,
   inputs ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.qb.4 <- lm_robust(data = md.moz,
   infrastructure ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

lm.moz.qb.6 <- lm_robust(data = md.moz,
   content_knowledge ~ quality_bureaucracy + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")

# explanatory = idm
lm.moz.idm.1 <- lm_robust(data = md.moz,
   student_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.idm.3 <- lm_robust(data = md.moz,
   inputs ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.idm.4 <- lm_robust(data = md.moz,
   infrastructure ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")
lm.moz.idm.6 <- lm_robust(data = md.moz,
   content_knowledge ~ impartial_decision_making + pct_urban + pct_lit + pct_schoolage + pct_elec + pct_dwell + ln_dist_n_stud +  as.factor(enrolled)  , clusters = g2, se_type = "stata")


```


## Regression Tables

### Overall 

```{r bi, warning=FALSE}
# table 1
tab_model(lm.bi.1, lm.bi.2, lm.bi.3, lm.bi.4, lm.bi.5, lm.bi.6,
          lm.bi.8, lm.bi.9, lm.bi.10,lm.bi.11,
          pred.labels = c("Bureaucracy Index", ivlabmain),
          dv.labels = dvlab,
          wrap.labels = 20,
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("bi", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>
```{r nlg, warning=FALSE}
# table 2
tab_model(lm.nlg.1, lm.nlg.2, lm.nlg.3, lm.nlg.4, lm.nlg.5, lm.nlg.6,
          lm.nlg.8, lm.nlg.9, lm.nlg.10,lm.nlg.11,
          pred.labels = c("National Learning Goals", ivlabmain),
          dv.labels = dvlab,
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("national_learning_goals", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>

```{r ma, warning=FALSE}
# table 1
tab_model(lm.ma.1, lm.ma.2, lm.ma.3, lm.ma.4, lm.ma.5, lm.ma.6,
          lm.ma.8, lm.ma.9, lm.ma.10,lm.ma.11,
          pred.labels = c("Mandates and Accountability", ivlabmain),
          dv.labels = dvlab,
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("mandates_accountability", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>


```{r qb, warning=FALSE}
# table 1
tab_model(lm.qb.1, lm.qb.2, lm.qb.3, lm.qb.4, lm.qb.5, lm.qb.6,
          lm.qb.8, lm.qb.9, lm.qb.10,lm.qb.11,
          pred.labels = c("Quality of Bureaucracy", ivlabmain),
          dv.labels = dvlab,
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("quality_bureaucracy", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>


```{r idm, warning=FALSE}
# table 1
tab_model(lm.idm.1, lm.idm.2, lm.idm.3, lm.idm.4, lm.idm.5, lm.idm.6,
          lm.idm.8, lm.idm.9, lm.idm.10,lm.idm.11,
          pred.labels = c("Impartial Decision-Making", ivlabmain),
          dv.labels = dvlab,
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("impartial_decision_making", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```

<br><br><br><br><br>


### Peru 

```{r per-bi, warning=FALSE}
# table 1
tab_model(lm.per.bi.1, lm.per.bi.2, lm.per.bi.3, lm.per.bi.4, lm.per.bi.5, lm.per.bi.6,
          lm.per.bi.8, lm.per.bi.9, lm.per.bi.10,lm.per.bi.11,
          pred.labels = c("Bureaucracy Index", ivlab),
          dv.labels = dvlab,
          wrap.labels = 20,
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("bi", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>
```{r per-nlg, warning=FALSE}
# table 2
tab_model(lm.per.nlg.1, lm.per.nlg.2, lm.per.nlg.3, lm.per.nlg.4, lm.per.nlg.5, lm.per.nlg.6,
          lm.per.nlg.8, lm.per.nlg.9, lm.per.nlg.10,lm.per.nlg.11,
          pred.labels = c("National Learning Goals", ivlab),
          dv.labels = dvlab,
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("national_learning_goals", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>

```{r per-ma, warning=FALSE}
# table 1
tab_model(lm.per.ma.1, lm.per.ma.2, lm.per.ma.3, lm.per.ma.4, lm.per.ma.5, lm.per.ma.6,
          lm.per.ma.8, lm.per.ma.9, lm.per.ma.10,lm.per.ma.11,
          pred.labels = c("Mandates and Accountability", ivlab),
          dv.labels = dvlab,
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("mandates_accountability", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r per-qb, warning=FALSE}
# table 1
tab_model(lm.per.qb.1, lm.per.qb.2, lm.per.qb.3, lm.per.qb.4, lm.per.qb.5, lm.per.qb.6,
          lm.per.qb.8, lm.per.qb.9, lm.per.qb.10,lm.per.qb.11,
          pred.labels = c("Quality of Bureaucracy", ivlab),
          dv.labels = dvlab,
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("quality_bureaucracy", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r per-idm, warning=FALSE}
# table 1
tab_model(lm.per.idm.1, lm.per.idm.2, lm.per.idm.3, lm.per.idm.4, lm.per.idm.5, lm.per.idm.6,
          lm.per.idm.8, lm.per.idm.9, lm.per.idm.10,lm.per.idm.11,
          pred.labels = c("Impartial Decision-Making", ivlab),
          dv.labels = dvlab,
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("impartial_decision_making", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```

<br><br><br><br><br>




### Jordan 

```{r jor-bi, warning=FALSE}
# table 1
tab_model(lm.jor.bi.1, lm.jor.bi.2, lm.jor.bi.3, lm.jor.bi.4, lm.jor.bi.5, lm.jor.bi.6,
          lm.jor.bi.8, lm.jor.bi.9, lm.jor.bi.10,lm.jor.bi.11,
          pred.labels = c("Bureaucracy Index", ivlab),
          dv.labels = dvlab,
          wrap.labels = 20,
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("bi", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>
```{r jor-nlg, warning=FALSE}
# table 2
tab_model(lm.jor.nlg.1, lm.jor.nlg.2, lm.jor.nlg.3, lm.jor.nlg.4, lm.jor.nlg.5, lm.jor.nlg.6,
          lm.jor.nlg.8, lm.jor.nlg.9, lm.jor.nlg.10,lm.jor.nlg.11,
          pred.labels = c("National Learning Goals", ivlab),
          dv.labels = dvlab,
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("national_learning_goals", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>

```{r jor-ma, warning=FALSE}
# table 1
tab_model(lm.jor.ma.1, lm.jor.ma.2, lm.jor.ma.3, lm.jor.ma.4, lm.jor.ma.5, lm.jor.ma.6,
          lm.jor.ma.8, lm.jor.ma.9, lm.jor.ma.10,lm.jor.ma.11,
          pred.labels = c("Mandates and Accountability", ivlab),
          dv.labels = dvlab,
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("mandates_accountability", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r jor-qb, warning=FALSE}
# table 1
tab_model(lm.jor.qb.1, lm.jor.qb.2, lm.jor.qb.3, lm.jor.qb.4, lm.jor.qb.5, lm.jor.qb.6,
          lm.jor.qb.8, lm.jor.qb.9, lm.jor.qb.10,lm.jor.qb.11,
          pred.labels = c("Quality of Bureaucracy", ivlab),
          dv.labels = dvlab,
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("quality_bureaucracy", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r jor-idm, warning=FALSE}
# table 1
tab_model(lm.jor.idm.1, lm.jor.idm.2, lm.jor.idm.3, lm.jor.idm.4, lm.jor.idm.5, lm.jor.idm.6,
          lm.jor.idm.8, lm.jor.idm.9, lm.jor.idm.10,lm.jor.idm.11,
          pred.labels = c("Impartial Decision-Making", ivlab),
          dv.labels = dvlab,
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("impartial_decision_making", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```

<br><br><br><br><br>




### Rwanda 

```{r rwa-bi, warning=FALSE}
# table 1
tab_model(lm.rwa.bi.1, lm.rwa.bi.2, lm.rwa.bi.3, lm.rwa.bi.4, lm.rwa.bi.5, lm.rwa.bi.6,
          lm.rwa.bi.8, lm.rwa.bi.9, lm.rwa.bi.10,lm.rwa.bi.11,
          pred.labels = c("Bureaucracy Index", ivlab),
          dv.labels = dvlab,
          wrap.labels = 20,
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("bi", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>
```{r rwa-nlg, warning=FALSE}
# table 2
tab_model(lm.rwa.nlg.1, lm.rwa.nlg.2, lm.rwa.nlg.3, lm.rwa.nlg.4, lm.rwa.nlg.5, lm.rwa.nlg.6,
          lm.rwa.nlg.8, lm.rwa.nlg.9, lm.rwa.nlg.10,lm.rwa.nlg.11,
          pred.labels = c("National Learning Goals", ivlab),
          dv.labels = dvlab,
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("national_learning_goals", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>

```{r rwa-ma, warning=FALSE}
# table 1
tab_model(lm.rwa.ma.1, lm.rwa.ma.2, lm.rwa.ma.3, lm.rwa.ma.4, lm.rwa.ma.5, lm.rwa.ma.6,
          lm.rwa.ma.8, lm.rwa.ma.9, lm.rwa.ma.10,lm.rwa.ma.11,
          pred.labels = c("Mandates and Accountability", ivlab),
          dv.labels = dvlab,
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("mandates_accountability", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r rwa-qb, warning=FALSE}
# table 1
tab_model(lm.rwa.qb.1, lm.rwa.qb.2, lm.rwa.qb.3, lm.rwa.qb.4, lm.rwa.qb.5, lm.rwa.qb.6,
          lm.rwa.qb.8, lm.rwa.qb.9, lm.rwa.qb.10,lm.rwa.qb.11,
          pred.labels = c("Quality of Bureaucracy", ivlab),
          dv.labels = dvlab,
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("quality_bureaucracy", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```
<br><br>


```{r rwa-idm, warning=FALSE}
# table 1
tab_model(lm.rwa.idm.1, lm.rwa.idm.2, lm.rwa.idm.3, lm.rwa.idm.4, lm.rwa.idm.5, lm.rwa.idm.6,
          lm.rwa.idm.8, lm.rwa.idm.9, lm.rwa.idm.10,lm.rwa.idm.11,
          pred.labels = c("Impartial Decision-Making", ivlab),
          dv.labels = dvlab,
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("impartial_decision_making", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud", "ln_gdp"))

```

<br><br><br><br><br>






### Mozambique 

```{r moz-bi, warning=FALSE}
# table 1
tab_model(lm.moz.bi.1, lm.moz.bi.3, lm.moz.bi.4,  lm.moz.bi.6,
          pred.labels = c("Bureaucracy Index", ivlabmoz),
          dv.labels = dvlabmoz,
          wrap.labels = 20,
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("bi", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>
```{r moz-nlg, warning=FALSE}
# table 2
tab_model(lm.moz.nlg.1, lm.moz.nlg.3, lm.moz.nlg.4,  lm.moz.nlg.6,
          pred.labels = c("National Learning Goals", ivlabmoz),
          dv.labels = dvlabmoz,
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("national_learning_goals", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>

```{r moz-ma, warning=FALSE}
# table 1
tab_model(lm.moz.ma.1, lm.moz.ma.3, lm.moz.ma.4,  lm.moz.ma.6,
          pred.labels = c("Mandates and Accountability", ivlabmoz),
          dv.labels = dvlabmoz,
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("mandates_accountability", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>


```{r moz-qb, warning=FALSE}
# table 1
tab_model(lm.moz.qb.1, lm.moz.qb.3, lm.moz.qb.4,  lm.moz.qb.6,
          pred.labels = c("Quality of Bureaucracy", ivlabmoz),
          dv.labels = dvlabmoz,
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("quality_bureaucracy", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```
<br><br>


```{r moz-idm, warning=FALSE}
# table 1
tab_model(lm.moz.idm.1, lm.moz.idm.3, lm.moz.idm.4,  lm.moz.idm.6,
          pred.labels = c("Impartial Decision-Making", ivlabmoz),
          dv.labels = dvlabmoz,
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          show.r2 = FALSE,
          p.style = "numeric",
          terms = c("impartial_decision_making", "pct_lit", "pct_urban", "pct_schoolage",
                    "pct_elec", "pct_dwell", "ln_dist_n_stud"))

```

<br><br><br><br><br>
