---
title: "Basic Regressions"
author: "Tom"
date: "September 1, 2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

#options(width = 300)

# packages 
library(tidyverse)
library(readstata13)
library(sjPlot)
library(shiny)

# object with outcome variables 
yvars <- c("student_knowledge",
           "ecd_student_knowledge",
           "inputs",
           "infrastructure",
           "intrinsic_motivation",
            "content_knowledge",
           "operational_manage",
           "instr_leader",
           "principal_knowl_score",
           "principal_manage",
           "bi",
           "national_learning_goals",
           "mandates_accountability",
           "quality_bureaucracy",
           "impartial_decision_making")

#load data 
md <- read.dta13(file = "C:/Users/WB551206/OneDrive - WBG/Documents/Dashboard/global-edu-dashboard/baseline/DataSets/final/merge_district_tdist.dta",
                 convert.factors = TRUE) %>%
  select(idschool, countryname, country, g1, g2, yvars)


```

# Introduction

This document presents bivariate OLS regressions with country-level fixed effects only, and the country coefficients are hidden. Note that Pedagogical Knowledge as a school outcome is excluded from analysis here because it is only captured in the Mozambique survey. Furthermore, the dataset used is slightly different than those used in the past, as this dataset uses the World Bank Polygons to determine the location -- and therefore, the attrition -- of observations. This results in a loss of about 40 school observations. I'm currently looking into what may be causing this, but my guess is that it may have to do with discrepencies in the shapes of regions in the two polygon datasets. 

## Main findings 
1. With the data we have,we see that the overall Bureaucracy Index it not a good predictor of any school outcomes, except for maybe school infrastructure. <br>
2. Signifant relationships among the secondary indicators are sparse, but what few there are are promising: <br>
  - National Learning Goals predict 2 variables related to instruction. <br>
  - Mandates and Accountability has a mild relationship with Student Knowledge <br>
  - Quality of Bureaucracy predicts infrastructure <br>
  - Impartial Decision-Making predicts 3 school-level indicators

```{r models,  include=FALSE}
# run + store all regressions regressions as objects

# explanatory = bi 
lm.bi.1 <- lm(data = md, 
   student_knowledge ~ bi + as.factor(countryname))
lm.bi.2 <- lm(data = md, 
   ecd_student_knowledge ~ bi + as.factor(countryname))
lm.bi.3 <- lm(data = md, 
   inputs ~ bi + as.factor(countryname))
lm.bi.4 <- lm(data = md, 
   infrastructure ~ bi + as.factor(countryname))
lm.bi.5 <- lm(data = md, 
   intrinsic_motivation ~ bi + as.factor(countryname))
lm.bi.6 <- lm(data = md, 
   content_knowledge ~ bi + as.factor(countryname))
lm.bi.8 <- lm(data = md, 
   operational_manage ~ bi + as.factor(countryname))
lm.bi.9 <- lm(data = md, 
   instr_leader ~ bi + as.factor(countryname))
lm.bi.10 <- lm(data = md, 
   principal_knowl_score ~ bi + as.factor(countryname))
lm.bi.11 <- lm(data = md, 
   principal_manage ~ bi + as.factor(countryname))

# explanatory = nlg 
lm.nlg.1 <- lm(data = md, 
   student_knowledge ~ national_learning_goals + as.factor(countryname))
lm.nlg.2 <- lm(data = md, 
   ecd_student_knowledge ~ national_learning_goals + as.factor(countryname))
lm.nlg.3 <- lm(data = md, 
   inputs ~ national_learning_goals + as.factor(countryname))
lm.nlg.4 <- lm(data = md, 
   infrastructure ~ national_learning_goals + as.factor(countryname))
lm.nlg.5 <- lm(data = md, 
   intrinsic_motivation ~ national_learning_goals + as.factor(countryname))
lm.nlg.6 <- lm(data = md, 
   content_knowledge ~ national_learning_goals + as.factor(countryname))
lm.nlg.8 <- lm(data = md, 
   operational_manage ~ national_learning_goals + as.factor(countryname))
lm.nlg.9 <- lm(data = md, 
   instr_leader ~ national_learning_goals + as.factor(countryname))
lm.nlg.10 <- lm(data = md, 
   principal_knowl_score ~ national_learning_goals + as.factor(countryname))
lm.nlg.11 <- lm(data = md, 
   principal_manage ~ national_learning_goals + as.factor(countryname))

# explanatory = ma
lm.ma.1 <- lm(data = md, 
   student_knowledge ~ mandates_accountability + as.factor(countryname))
lm.ma.2 <- lm(data = md, 
   ecd_student_knowledge ~ mandates_accountability + as.factor(countryname))
lm.ma.3 <- lm(data = md, 
   inputs ~ mandates_accountability + as.factor(countryname))
lm.ma.4 <- lm(data = md, 
   infrastructure ~ mandates_accountability + as.factor(countryname))
lm.ma.5 <- lm(data = md, 
   intrinsic_motivation ~ mandates_accountability + as.factor(countryname))
lm.ma.6 <- lm(data = md, 
   content_knowledge ~ mandates_accountability + as.factor(countryname))
lm.ma.8 <- lm(data = md, 
   operational_manage ~ mandates_accountability + as.factor(countryname))
lm.ma.9 <- lm(data = md, 
   instr_leader ~ mandates_accountability + as.factor(countryname))
lm.ma.10 <- lm(data = md, 
   principal_knowl_score ~ mandates_accountability + as.factor(countryname))
lm.ma.11 <- lm(data = md, 
   principal_manage ~ mandates_accountability + as.factor(countryname))


# explanatory = qb
lm.qb.1 <- lm(data = md, 
   student_knowledge ~ quality_bureaucracy + as.factor(countryname))
lm.qb.2 <- lm(data = md, 
   ecd_student_knowledge ~ quality_bureaucracy + as.factor(countryname))
lm.qb.3 <- lm(data = md, 
   inputs ~ quality_bureaucracy + as.factor(countryname))
lm.qb.4 <- lm(data = md, 
   infrastructure ~ quality_bureaucracy + as.factor(countryname))
lm.qb.5 <- lm(data = md, 
   intrinsic_motivation ~ quality_bureaucracy + as.factor(countryname))
lm.qb.6 <- lm(data = md, 
   content_knowledge ~ quality_bureaucracy + as.factor(countryname))
lm.qb.8 <- lm(data = md, 
   operational_manage ~ quality_bureaucracy + as.factor(countryname))
lm.qb.9 <- lm(data = md, 
   instr_leader ~ quality_bureaucracy + as.factor(countryname))
lm.qb.10 <- lm(data = md, 
   principal_knowl_score ~ quality_bureaucracy + as.factor(countryname))
lm.qb.11 <- lm(data = md, 
   principal_manage ~ quality_bureaucracy + as.factor(countryname))

# explanatory = idm
lm.idm.1 <- lm(data = md, 
   student_knowledge ~ impartial_decision_making + as.factor(countryname))
lm.idm.2 <- lm(data = md, 
   ecd_student_knowledge ~ impartial_decision_making + as.factor(countryname))
lm.idm.3 <- lm(data = md, 
   inputs ~ impartial_decision_making + as.factor(countryname))
lm.idm.4 <- lm(data = md, 
   infrastructure ~ impartial_decision_making + as.factor(countryname))
lm.idm.5 <- lm(data = md, 
   intrinsic_motivation ~ impartial_decision_making + as.factor(countryname))
lm.idm.6 <- lm(data = md, 
   content_knowledge ~ impartial_decision_making + as.factor(countryname))
lm.idm.8 <- lm(data = md, 
   operational_manage ~ impartial_decision_making + as.factor(countryname))
lm.idm.9 <- lm(data = md, 
   instr_leader ~ impartial_decision_making + as.factor(countryname))
lm.idm.10 <- lm(data = md, 
   principal_knowl_score ~ impartial_decision_making + as.factor(countryname))
lm.idm.11 <- lm(data = md, 
   principal_manage ~ impartial_decision_making + as.factor(countryname))

```

## Regression Tables

```{r bi}
# table 1
tab_model(lm.bi.1, lm.bi.2, lm.bi.3, lm.bi.4, lm.bi.5, lm.bi.6, lm.bi.8, lm.bi.9, lm.bi.10,lm.bi.11,
          pred.labels = c("Bureaucracy Index"),
          title = "Bureaucracy Index",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          p.style = "stars",
          terms = c("bi"))

```

```{r nlg}
# table 1
tab_model(lm.nlg.1, lm.nlg.2, lm.nlg.3, lm.nlg.4, lm.nlg.5, lm.nlg.6, lm.nlg.8, lm.nlg.9, lm.nlg.10,lm.nlg.11,
          pred.labels = c("National Learning Goals"),
          title = "National Learning Goals",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          p.style = "stars",
          terms = c("national_learning_goals"))

```

```{r ma}
# table 1
tab_model(lm.ma.1, lm.ma.2, lm.ma.3, lm.ma.4, lm.ma.5, lm.ma.6, lm.ma.8, lm.ma.9, lm.ma.10,lm.ma.11,
          pred.labels = c("Mandates + Acct'y"),
          title = "Mandates and Accountability",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          p.style = "stars",
          terms = c("mandates_accountability"))

```


```{r qb}
# table 1
tab_model(lm.qb.1, lm.qb.2, lm.qb.3, lm.qb.4, lm.qb.5, lm.qb.6, lm.qb.8, lm.qb.9, lm.qb.10,lm.qb.11,
          pred.labels = c("Qual. of Bureaucracy"),
          title = "Quality of Bureaucracy",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          p.style = "stars",
          terms = c("quality_bureaucracy"))

```


```{r idm}
# table 1
tab_model(lm.idm.1, lm.idm.2, lm.idm.3, lm.idm.4, lm.idm.5, lm.idm.6, lm.idm.8, lm.idm.9, lm.idm.10,lm.idm.11,
          pred.labels = c("Impar. Dec'n-Making"),
          title = "Impartial Decision-Making",
          show.ci = FALSE,
          show.se = TRUE,
          collapse.se = TRUE,
          linebreak = TRUE,
          show.intercept = FALSE,
          p.style = "stars",
          terms = c("impartial_decision_making"))

```


### Interactive By-Country Visualizations
Select up to two pairs of explanatory variables (Bureaucracy Indicators) and Outcomes Variables (School Outcomes) to visualize the scatterplots and best-fit lines by country.

####Variable Selector
Plot 1
```{r}


# inputs 1
selectInput("yvar1", #inputid
            "Outcome Variable 1", #label
           choices = c("Student Knowledge" = "student_knowledge",
           "1st Grade Student Knowledge" = "ecd_student_knowledge",
           "Inputs" = "inputs",
           "Infrastructure" = "infrastructure",
           "Teacher Motivation" = "intrinsic_motivation",
           "Teacher Content Knowledge" = "content_knowledge",
           "Operational Management" = "operational_manage",
           "Instructional Leadership" = "instr_leadership",
           "Principal Knolwedge Score" = "principal_knowl_score",
           "Principal Management" = "principal_manage"),
           multiple = FALSE,
           selected = "infrastructure"
)
           
selectInput("xvar1", #inputid
            "Explanatory Variable 1", #label
           choices = c("Bureaucracy Index" = "bi",
                       "National Learning Goals" = "national_learning_goals",
                       "Mandates and Accountability" = "mandates_accountability",
                       "Quality of Bureaucracy" = "quality_bureaucracy",
                       "Impartial Decision-Making" = "impartial_decision_making"),
           multiple = FALSE,
           selected = "bi"
)
```



Plot 2
```{r}
# inputs 2
selectInput("yvar2", #inputid
            "Outcome Variable 2", #label
           choices = c("Student Knowledge" = "student_knowledge",
           "1st Grade Student Knowledge" = "ecd_student_knowledge",
           "Inputs" = "inputs",
           "Infrastructure" = "infrastructure",
           "Teacher Motivation" = "intrinsic_motivation",
           "Teacher Content Knowledge" = "content_knowledge",
           "Operational Management" = "operational_manage",
           "Instructional Leadership" = "instr_leadership",
           "Principal Knolwedge Score" = "principal_knowl_score",
           "Principal Management" = "principal_manage"),
           multiple = FALSE,
           selected = "content_knowledge"
)
           
selectInput("xvar2", #inputid
            "Explanatory Variable 2", #label
           choices = c("Bureaucracy Index" = "bi",
                       "National Learning Goals" = "national_learning_goals",
                       "Mandates and Accountability" = "mandates_accountability",
                       "Quality of Bureaucracy" = "quality_bureaucracy",
                       "Impartial Decision-Making" = "impartial_decision_making"),
           multiple = FALSE,
           selected = "national_learning_goals"
)



```


Plot 1
```{r, fig.align='center', fig.show='hold'}

# plot 1
renderPlot({
  # make the plot 
 ggplot(md, aes_string(input$xvar1, input$yvar1)) +
    geom_jitter() +
    geom_smooth(method = lm) +
    facet_wrap(~ countryname)
  
},
# plot options
  width  = 500,
  height = 400,
  res = 100
)


```

Plot 2

```{r}



# plot 2         
renderPlot({
  # make the plot 
 ggplot(md, aes_string(input$xvar2, input$yvar2)) +
    geom_jitter() +
    geom_smooth(method = lm) +
    facet_wrap(~ countryname)
  
},
# plot options
  width  = 500,
  height = 400,
  res = 100
)



```
 